Night and day: The influence and relative importance of urban characteristics on remotely sensed land surface temperature

### 2020-05-05 report/article.tex

\subsection{Land surface temperature (dependent variable)}
We calculate land surface temperature using Landsat 8 (Land Processes Distributed Active Archive Center product) imagery, land cover data, and an air temperature observation (data sources provided in \ref{tab:data}). 
Our code is available on our Github\footnote{URL redacted for review} repository, and follows the process described in \cite{Scott2016-lc}:
\begin{itemize}
    \item 
        Convert Band-10 digital-number data to top-of-atmosphere radiance \citep{Jimenez-Munoz2003-wc}: 
        \begin{equation}
        \label{eqn:convert_TOA}
        L_\lambda = M_L Q_{cal} + A_L
        \end{equation}
        where:
        \begin{conditions}
         L_\lambda & Top-of-atmosphere spectral radiance \\
         M_L &  Band-specific multiplicative rescaling factor from the satellite metadata \\   
         A_L &  Band-specific additive rescaling factor from the satellite metadata \\   
         Q_{cal} &  Quantized and calibrated standard product pixel values
        \end{conditions}
    \item Determine the emissivity using land cover data \citep{Alipour2003-ym}, and then calculate the at-satellite brightness temperature \citep{Jimenez-Munoz2003-wc}: 
        \begin{equation}
        \label{eqn:at_sat}
        T_s = \frac{K_2}{ln(1 + \frac{K_1}{L})}
        \end{equation}
        where:
        \begin{conditions}
         T_s & At-satellite brightness temperature \\
         L &  Spectral radiance ($L_\lambda$) divided by the emissivity \\   
         K_1, K_2 & Band-specific thermal conversion constants from the satellite metadata
        \end{conditions}
    \item Correct the brightness temperature for atmospheric water vapor using the mono-window algorithm \citep{Qin2001-jn} using the maximum observed temperature of the day from a nearby weather station (see the code in \ref{appendix:code}).
\end{itemize}
The result is a geospatial dataset of land surface temperature at a 100-meter resolution.

@@

% Here are two sample references: \citep{Feynman1963118,Dirac1953888}.
\section*{Acknowledgements}
% TML conducted the majority of this research as a graduate student at the University of Michigan with the support of a Rackham PreDoctoral Fellowship.
% The work was also supported by the US National Science Foundation's Grant SEES-1631409. 
% This support is gratefully acknowledged.

@@

This is an extract of the code provided in the GitHub repository: []

>>>>

\subsection{Land surface temperature (dependent variable)}
We calculate land surface temperature using Landsat 8 (Land Processes Distributed Active Archive Center product) imagery, land cover data, and an air temperature observation (data sources provided in \ref{tab:data}). 
Our code is available on our Github\footnote{\url{https://github.com/tommlogan/land_surface_temperature}} repository, and follows the process described in \cite{Scott2016-lc}:
\begin{itemize}
    \item 
        Convert Band-10 digital-number data to top-of-atmosphere radiance \citep{Jimenez-Munoz2003-wc}: 
        \begin{equation}
        \label{eqn:convert_TOA}
        L_\lambda = M_L Q_{cal} + A_L
        \end{equation}
        where:
        \begin{conditions}
         L_\lambda & Top-of-atmosphere spectral radiance \\
         M_L &  Band-specific multiplicative rescaling factor from the satellite metadata \\   
         A_L &  Band-specific additive rescaling factor from the satellite metadata \\   
         Q_{cal} &  Quantized and calibrated standard product pixel values
        \end{conditions}
    \item Determine the emissivity using land cover data \citep{Alipour2003-ym}, and then calculate the at-satellite brightness temperature \citep{Jimenez-Munoz2003-wc}: 
        \begin{equation}
        \label{eqn:at_sat}
        T_s = \frac{K_2}{ln(1 + \frac{K_1}{L})}
        \end{equation}
        where:
        \begin{conditions}
         T_s & At-satellite brightness temperature \\
         L &  Spectral radiance ($L_\lambda$) divided by the emissivity \\   
         K_1, K_2 & Band-specific thermal conversion constants from the satellite metadata
        \end{conditions}
    \item Correct the brightness temperature for atmospheric water vapor using the mono-window algorithm \citep{Qin2001-jn} using the maximum observed temperature of the day from a nearby weather station (see the code in \ref{appendix:code}).
\end{itemize}
The result is a geospatial dataset of land surface temperature at a 100-meter resolution.

@@

% Here are two sample references: \citep{Feynman1963118,Dirac1953888}.
\section*{Acknowledgements}
The work was funded by the US National Science Foundation's Grant SEES-1631409 and a University of Michigan Rackham PreDoctoral Fellowship. 
This support is gratefully acknowledged.

@@

This is an extract of the code provided in the GitHub repository: \url{https://github.com/tommlogan/land_surface_temperature}
